---
title: "Tutorial: Artifact Repository"
author: "Lukasz A. Bartnik"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial: Artifact Repository}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(knitr)

knitr::opts_chunk$set(collapse = TRUE, comment = "#>", prompt = FALSE, echo = TRUE)
```


# Produce objects - sample research project

Run a sample project generation.


# Basic operations

## Project overview

We can look at R sessions recorded so far:

```{r}
objects$session
```

We can also see objects recorded in the repository:

```{r}
objects$name
```

Other keys are: `class`, `id` and `time`. Let's look at `time`:

```{r}
objects$time
```


## Limiting the selection

We can limit the object selection by session identifier:

```{r}
objects$session$eba8e78f
```

Similarily, we can look at specific object creation time:

```{r}
objects$time$since_yesterday
```

In both cases, we see a `filter()` expression added to the selection
query and at most the first three objects matching this query.


## Selecting an object

Finally, we can retrieve a specific object from the repository:

```{r}
objects$name$x
```

